---
title: "ETO5513 Assessment 1 - Data Mini Project"
author: "Gun Ho Jang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include =  FALSE, message = FALSE, warning = FALSE}
# Loading libraries for the project
library(tidyverse)
library(countrycode)
library(knitr)
```

## Research Question

In recent years, the rising cost of living crisis has represented a particularly cumbersome period for economies worldwide as inflationary pressures on the price of food and energy have pushed households and businesses to the brink (Whiting, 2022; Shipman et al., 2023). Rising food prices in particular have consequentially affected a large number of people and their financial ability to afford groceries. This project will investigate this matter of food insecurity, and consider the following: how much of the population globally are unable to afford a healthy diet?

a large number of people have become increasingly exposed to food affordability issues. This project will investigate the matter of food insecurity, and consider the following: how much of the population across the globe are at risk of not affording a healthy diet?



## References

Whiting, K. (2022, September 21). *The cost-of-living crisis is having a global impact. Here's what countries are doing to help.* World Economic Forum. <https://www.weforum.org/stories/2022/09/cost-of-living-crisis-global-impact/>

Shipman, A., Smondel, A., Adhinegara, B. Y., Diamond, J. W., Vega, L. G., Shahrour, M. H., Martin, P. & Simpson, W. (2023, January 7). *Global economy 2023: how countries around the world are tackling the cost of living crisis*. The Conversation. <https://theconversation.com/global-economy-2023-how-countries-around-the-world-are-tackling-the-cost-of-living-crisis-196740>
